### 2021-06-07 README.Rmd
updated package citation; added to README

>>>>

**Barneche DR, Coleman G, Fermor D, Klein E, Robinson T, Smith J, Sheehan JL, Dowley S, Ditton D, Gunn K, Ericson G, Logan M, Rehbein M** (2021). dataaimsr: An R Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform. *Journal of Open Source Software*, **6:** 3282. doi: [10.21105/joss.03282](https://doi.org/10.21105/joss.03282).
